Evaluation of the repository

### 2024-11-21 pages/repo_evaluation.qmd
feat(badges): create table for article

@@

>>>>

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
badges_dict = {
  'open_acm': [1, 0, 7, 0],
  'open_niso': [1, 0, 7, 0],
  'open_niso_all': [0, 0, 8, 0],
  'open_cos': [1, 0, 7, 0],
  'open_ieee': [1, 0, 7, 0],
  'review_acm_functional': [0, 0, 8, 0],
  'review_acm_reusable': [0, 0, 8, 0],
  'review_ieee': [1, 0, 7, 0],
  'reproduce_acm': [1, 0, 7, 0],
  'reproduce_niso': [1, 0, 7, 0],
  'reproduce_ieee': [1, 0, 7, 0],
  'reproduce_psy': [0, 0, 8, 0],
}
badges_wide = pd.DataFrame(badges_dict, index=col).T

# Full badge names
badge_names = {
    # Open objects
    'open_acm': 'ACM “Artifacts<br>Available”',
    'open_niso': 'NISO “Open Research<br>Objects (ORO)”',
    'open_niso_all': 'NISO “Open Research<br>Objects - All (ORO-A)”',
    'open_cos': 'COS “Open Code”',
    'open_ieee': 'IEEE “Code Available”',
    # Object review
    'review_acm_functional': 'ACM “Artifacts<br>Evaluated - Functional”',
    'review_acm_reusable': 'ACM “Artifacts<br>Evaluated - Reusable”',
    'review_ieee': 'IEEE “Code Reviewed”',
    # Results reproduced
    'reproduce_acm': 'ACM “Results Reproduced”',
    'reproduce_niso': 'NISO “Results<br>Reproduced (ROR-R)”',
    'reproduce_ieee': 'IEEE “Code Reproducible”',
    'reproduce_psy': 'Psychological Science<br>“Computational Reproducibility”'
}

# Replace with full badge names
badges_fig = badges_wide.copy()
badges_fig.index = badges_fig.index.map(badge_names)

# Create figure
eval_chart(badges_fig)
```

@@

## Badges summary tables for the article

```{python}
# Criteria and their definitions
criteria = {
    'archive': 'Artefacts are archived in a repository that is: (a) public (b) guarantees persistence (c) gives a unique identifier (e.g. DOI)',
    'licence': 'Open licence',
    'complete': 'Complete (all relevant artefacts available)',
    'docs1': 'Documents (a) how code is used (b) how it relates to article (c) software, systems, packages and versions',
    'docs2': 'Documents (a) inventory of artefacts (b) sufficient description for artefacts to be exercised',
    'relevant': 'Artefacts relevant to paper',
    'execute': 'Scripts can be successfully executed',
    'careful': 'Artefacts are carefully documented and well-structured to the extent that reuse and repurposing is facilitated, adhering to norms and standards',
    'reproduce': 'Reproduced results (assuming (a) acceptably similar (b) reasonable time frame (c) only minor troubleshooting)',
    'readme': 'README file with step-by-step instructions to run analysis',
    'dependencies': 'Dependencies (e.g. package versions) stated',
    'correspond': 'Clear how output of analysis corresponds to article'
}

# Criteria required by each badge
badges = {
    # Open objects
    'open_acm': ['archive'],
    'open_niso': ['archive', 'licence'],
    'open_niso_all': ['archive', 'licence', 'complete'],
    'open_cos': ['archive', 'licence', 'docs1'],
    'open_ieee': ['complete'],
    # Object review
    'review_acm_functional': ['docs2', 'relevant', 'complete', 'execute'],
    'review_acm_reusable': ['docs2', 'relevant', 'complete', 'execute', 'careful'],
    'review_ieee': ['complete', 'execute'],
    # Results reproduced
    'reproduce_acm': ['reproduce'],
    'reproduce_niso': ['reproduce'],
    'reproduce_ieee': ['reproduce'],
    'reproduce_psy': ['reproduce', 'readme', 'dependencies', 'correspond']
}

# Find proportion fully met, then use to make "met criteria" column
badges_table = badges_wide.copy()
badges_table['percent'] = round((badges_table['fully'] / 8)*100, 2)
badges_table['met_criteria'] = badges_table['fully'].astype(str) + '/8 (' + badges_table['percent'].astype(str) + '%)'

# Create a column with criteria for each badge
badges_table['criteria'] = badges_table.index.map(
    lambda badge: '<br>'.join(
        f"• {criteria[crit]}" for crit in badges[badge]
    )
)

# Replace with full badge names, then filter and relabel columns
badges_table.index = badges_table.index.map(badge_names)
badges_table.index.name = 'Badge'
badges_table = badges_table[['criteria', 'met_criteria']].rename(
  columns={'criteria': 'Criteria', 'met_criteria': 'Studies that met criteria'}
)
badges_table
```
